### 2009-12-19 trunk/Papers/reasoning-challenges/levels.tex
done

While this format for the IPC has been highly successful in the past
ten years, there is also a number of ways in which it can be improved and
streamlined.  One such direction concerns the way in which problem classes
are collected.  There is no doubt that the existing collection of IPC
domains is a fundamental driving force for the development of new planning
algorithms.  Unfortunately, the current selection process makes it
difficult for users of these systems, who may come from different
communities, to get a new application-motivated domain accepted as an IPC
benchmark.  This is unsurprising, given that IPC organizers must be able to
justify their selection of domains, and picking untested domains from other
communities is not the best way to do this.  However, this leads to a
selection process that is less dynamic than it could be, and more
restrictive for users wanting to contribute suggestions.  Conversely, to
keep the number of domains that must be tested in each round of the
competition manageable, older domains are sometimes ``retired'', i.e.\
removed from subsequent competitions.  This comes with a risk of a false
sense of progress, in which retired domains are remembered as ``solved''
although they were removed for completely independent reasons.  Finally, it
has been argued \cite{ToughNuts} that some IPC organizers tend to favor the
development of new types of planning problems and new dialects of PDDL over
trying to find challenging benchmark problems for existing versions of
PDDL. Such approaches run the risk of ``reinventing'' past problem classes
(albeit in different guises), or redirecting investigation away from
current challenges.

@@

Of course, several issues need to be addressed to make this possible.
The first is how we can allow users to upload their systems and still
expect to run and maybe compile them automatically, without requiring
the manual intervention of an organizer if things break.  This problem
can be solved by imposing strict requirements on the execution
environment of the planner.  One way in which we could envision this
is by defining a single image for a virtual machine, such as
VirtualBox.\footnote{\url{http://www.virtualbox.org/}} When a planner
is evaluated, this happens in a fresh instance of this virtual
machine.  We can offer the virtual machine image for download; a
participant can then run the image on their own machine and ensure
that their planner works, in the exact environment in which it will be
evaluated.  This would even make it technically possible for
participants to submit not the source code, but a binary executable of
the planner (perhaps along with support files).  However, even if we
require the submission of source code, the move to a clean virtual
machine environment that contains only standard versions of tools and
libraries enforces at least a certain degree of portability from which
users will benefit when they download the planners.  Even when the
virtual machine image changes to reflect updates in the standard
development environments (new version of the C compiler, etc.), old
images could remain available, and so old planners would continue
running until the virtual machine emulator itself becomes unavailable
or incompatible.

We propose that every newly submitted planner is run automatically on
all available problem instances, and every newly submitted problem
instance is sent to all available planners.  The scheduling of this
process can be under the control of an automated system for continuous
integration, such as Hudson.\footnote{\url{http://hudson-ci.org/}}
Each run of a planner on a problem instance or problem class can take
place in a fresh instance of the virtual machine image.  The
evaluation infrastructure then inserts the problem data and the
planner into the virtual machine, runs the planner, measures
performance statistics (including which problems they could solve and
how much time this took them; see below), and stores the results in a
database.  Users will be able to view the results in dynamically
generated reports on the main website; there may also be functionality to
customize these reports to focus on certain types of problems.  Because all
planners are run on all problem instances, and users can ensure that
challenging problem instances are included in the competition, the chance
of systems being evaluated on only a small and somewhat arbitrary selection
of certain problems \cite{pg2008002} can be avoided.

In order to minimize security risks, which can arise when user-submitted
programs are being run automatically, the individual virtual
machines need to be sandboxed quite tightly.  There is no need for an
individual virtual machine to be connected to any network, beyond
being able to enter performance measurements into a database.  By
further imposing resource limits on the number of available
processors, memory and processor time, and disk space, we believe the
potential for abuse is limited.  It can be limited further by only
allowing planner uploads to registered users.

While we see our proposed system's ability to generate up-to-date
reports automatically as a major strength, there may still be a
benefit in maintaining the current style of regular competitions at
discrete timepoints, e.g., to encourage the development of faster
planners through awards.  Such a competition could easily be based on
our system, by announcing a deadline and a specified subset of problem
classes. The selection of this subset could be informed, among other
things, by the report on problems that many planners can't
solve. Participants could then upload their planners at their leisure;
``running'' the competition amounts to taking a snapshot of the
performance reports on the selected problems when the deadline comes
and announcing the results.  By recording timestamps whenever a
performance measurements is made, this snapshot could remain available
on the website simply as one special report for a certain point in
time.  In such a case, the authors of planners should have the option
of marking them as ``non-competing'' to exclude them from the
competition snapshot, and maybe also from the up-to-date performance
reports.

@@

The simplest such mechanism is to add Wiki pages to the evaluation
website.  This would allow the users who upload problem classes to
document these problems and link to existing literature; it would
allow the developers of planners to document these planners; and it
would make it easy for the organizers of regular competitions to add
more information to the snapshot reports.  The exchange of ideas and
opinions can be further facilitated by providing a discussion board
which links into these Wiki pages.

A second social networking tool which we believe would be useful in
the context of a planning evaluation website is to let users tag
problem classes and vote on them.  Any registered user can be allowed
to comment on any problem class and vote for how relevant, important,
or exciting they find it -- say, using a one to five star system as on
Amazon.  This has a number of crucial advantages.  First, an incoming
user or a competition organizer can take the average score as an
indication for the problems that are considered important in the
community; imagine a ``top ten'' list of domains and planners on the
website's front page.  Next to the difficulty of problems, this can be
another factor in the selection of problem classes for a competition
snapshot.  Second, a relevance score for problem classes can also
serve as a guideline for the scheduling of planner runs: Assuming that
there is not enough computing power to run all incoming planners on
all domains in real time (e.g., just before a competition deadline),
the runs on popular domains can be prioritized.

@@

The continuous evaluation infrastructure we just presented is
fundamentally agnostic to the type of concrete evaluation measures
that it collects.  In particular, traditional measures such as the
percentage of problems solved per system, average solution quality,
average runtime and memory use, and search tree sizes can be
collected -- with the caveat that the virtual machine must be
configured so as to allow comparable runtime measurements.
Furthermore, popularity scores from the social networking aspect can
be incorporated, or different measures could be combined into an
overall score.

@@

We believe that the actual hardware cost will be bearable.  While the
idea of running all planners on all domains sounds intimidating at
first, we don't anticipate that there will ever be more than a couple
dozen current versions of planners entered in the system.  This means
that any new domain that is entered will not be attempted to be solved
too many times.  Conversely, while there may (hopefully!) be a
significant number of domains in the system, and every new planner
must try to solve all domains whose types it claims to be able to
process, this cost can also be controlled by prioritizing popular or
hard domains.  A single computer should be sufficient for these needs;
if it turns out not to be, the virtual machines can easily be run on
machines anywhere.

@@

One advantage of the evaluation infrastructure proposed above is that
its applicability is not limited to the evaluation of planners.
%RP: I don't see why this needs to be restricted to "reasoning" tasks
Many reasoning tasks, including constraint solving and theorem proving, are
being evaluated by running solvers over problem instances and reporting
performance measures.  At the level of abstraction at which our continuous
evaluation system could be implemented, there is no fundamental difference
between the problem type ``deterministic planning problem in PDDL 1.0'' and
the problem type ``\todo{something from CP or similar}'' -- in both cases,
the system can collect problem classes and instances of this type and run
them through solvers that declare themselves to accept such inputs.  This
means that there is a potential for sharing development and maintenance
costs for the evaluation platform among different communities.

However, there are of course limitations to the type of problem for
which it makes sense to run a community-driven continuous evaluation.
For one thing, it must be acceptable in the community that every
system runs on the same hardware and software configuration, as
implemented in the virtual machine images.  On the other hand, our
system makes most sense where the ratio of problem classes to systems
is relatively high.  Neither of the two is true, for instance, for
most natural language processing competitions: different research
groups tend to use a variety of programming languages and development
environments to build their systems, and there are typically many more
systems in any competition than there are problem classes (corpora).
However, our approach is completely consistent with the requirements
of a community where solving a single hard problem instance for the
first time counts as an achievement, such as in theorem proving.

>>>>

While this format for the IPC has been highly successful in the past
ten years, there is also a number of ways in which it can be improved
and streamlined.  One such direction concerns the way in which problem
classes are collected.  There is no doubt that the existing collection
of IPC domains is a fundamental driving force for the development of
new planning algorithms.  Unfortunately, the current selection process
makes it difficult for users of these systems, who may come from
different communities, to get a new application-motivated domain
accepted as an IPC benchmark.  This is unsurprising, given that IPC
organizers must be able to justify their selection of domains, and
picking untested domains from other communities is not the best way to
do this.  However, this leads to a selection process that is less
dynamic than it could be, and more restrictive for users wanting to
contribute suggestions.  Conversely, to keep the number of domains
that must be tested in each round of the competition manageable, older
domains are sometimes ``retired'', i.e.\ removed from subsequent
competitions.  This comes with a risk of a false sense of progress, in
which retired domains are remembered as ``solved'' although they were
removed for completely independent reasons.  Finally, it has been
argued \cite{ToughNuts} that IPC organizers may be tempted to favor
the development of new types of planning problems and new dialects of
PDDL over trying to find challenging benchmark problems for existing
versions of PDDL. Such approaches run the risk of ``reinventing'' past
problem classes (albeit in different guises), or redirecting
investigation away from current challenges.

@@

Of course, several issues need to be addressed to make this possible.
The first is how we can allow users to upload their systems and still
expect to run and maybe compile them automatically, without requiring
the manual intervention of an organizer if things break.  This problem
can be solved by imposing strict requirements on the execution
environment of the planner.  One way in which we could envision this
is by defining a single hardware and software environment in which
systems will be evaluated, and making it available for download as a
virtual machine image.  Developers can then run this image on their
own machine, using a virtual machine such as
VirtualBox,\footnote{\url{http://www.virtualbox.org/}} and ensure
that their system works, in the exact environment in which it will be
evaluated.  This would even make it technically possible for
participants to submit not the source code, but a binary executable
(perhaps along with support files).  However, even if we require the
submission of source code, the move to a precisely defined environment
that contains only standard versions of tools and libraries and on
which the code must compile without human intervention enforces at
least a certain degree of portability from which users will benefit
when they download the systems.  Even when the environment changes to
reflect updates in the standard development environments (new version
of the C compiler, etc.), old images could remain available, and so
old systems would continue running until the virtual machine emulator
itself becomes unavailable or incompatible.

We propose that every newly submitted system is run automatically on
all available problem instances, and every newly submitted problem
instance is sent to all available systems.  The scheduling of this
process can be under the control of an automated system for continuous
integration, such as Hudson.\footnote{\url{http://hudson-ci.org/}} The
evaluation infrastructure sends the problem data and the system to the
test machine, runs the system, measures performance statistics
(including which problems they could solve and how much time this took
them; see below), and stores the results in a database. Users will be
able to view the results in dynamically generated reports on the main
website; there may also be functionality to customize these reports to
focus on certain types of problems.  Because all systems are run on
all problem instances, and users can ensure that challenging problem
instances are included in the competition, the chance of systems being
evaluated on only a small and somewhat arbitrary selection of problem
instances \cite{pg2008002} can be avoided.

In order to minimize security risks, which can arise when
user-submitted programs are being run automatically, the test machines
need to be sandboxed quite tightly.  In particular, the machines do
not need to be able to initiate any network connections, beyond being
able to enter performance measurements into a database, and can work
on virtual file systems that are deleted after each system.  By
further imposing resource limits on the number of available
processors, memory and processor time, and disk space, we believe the
potential for abuse is limited.  It can be limited further by only
allowing systems uploads to registered users.

While we see our proposed system's ability to generate up-to-date
reports automatically as a major strength, there may still be a
benefit in maintaining the current style of regular competitions at
discrete timepoints, e.g., to encourage the development of faster
systems through awards.  Such a competition could easily be based on
our system, by announcing a deadline and a specified subset of problem
classes. The selection of this subset could be informed, among other
things, by the report on problems that many systems can't
solve. Participants could then upload their systems at their leisure;
``running'' the competition amounts to taking a snapshot of the
performance reports on the selected problems when the deadline comes
and announcing the results.  By recording timestamps whenever a
performance measurements is made, this snapshot could remain available
on the website simply as one special report for a certain point in
time.  In such a case, the authors of systems should have the option
of marking them as ``non-competing'' to exclude them from the
competition snapshot, and maybe also from the up-to-date performance
reports.

@@

The simplest such mechanism is to add Wiki pages to the evaluation
website.  This would allow the users who upload problem classes to
document these problems and link to existing literature; it would
allow the developers of systems to document these systems; and it
would make it easy for the organizers of regular competitions to add
more information to the snapshot reports.  The exchange of ideas and
opinions can be further facilitated by providing a discussion board
which links into these Wiki pages.

A second social networking tool which we believe would be useful in
the context of a planning evaluation website is to let users tag
problem classes and vote on them.  Any registered user can be allowed
to comment on any problem class and vote for how relevant, important,
or exciting they find it -- say, using a one to five star system as on
Amazon.  This has a number of crucial advantages.  First, an incoming
user or a competition organizer can take the average score as an
indication for the problems that are considered important in the
community; imagine a ``top ten'' list of problem classes and systems
on the website's front page.  Next to the difficulty of problems, this
can be another factor in the selection of problem classes for a
competition snapshot.  Second, a relevance score for problem classes
can also serve as a guideline for the scheduling of system runs:
Assuming that there is not enough computing power to run all incoming
planners on all problem instances in real time (e.g., just before a
competition deadline), the runs on popular domains can be prioritized.

@@

The continuous evaluation infrastructure we just presented is
fundamentally agnostic to the type of concrete evaluation measures
that it collects.  In particular, traditional measures such as the
percentage of problems solved per system, average solution quality,
average runtime and memory use, and search tree sizes can be collected
-- with the caveat that the test machines must be configured so as to
allow comparable runtime measurements.  Furthermore, popularity scores
from the social networking aspect can be incorporated, or different
measures could be combined into an overall score.

@@

We believe that the actual hardware cost will be bearable.  While the
idea of running all systems on all problem instances sounds
intimidating at first, we don't anticipate that there will ever be
more than a couple dozen current versions of systems entered in the
evaluation process.  This means that any new domain that is entered
will not be attempted to be solved too many times.  Conversely, while
there may (hopefully!) be a significant number of domains in the
system, and every new system must try to solve all problem instances
whose types it claims to be able to process, this cost can also be
controlled by prioritizing popular or hard domains.  A single computer
should be sufficient for these needs for the most part; in times of
high demand (e.g., just before a competition deadline), the work can
be automatically distributed over ``slave'' test machines by an
off-the-shelf continuous integration engine.

@@

One advantage of the evaluation infrastructure proposed above is that
its applicability is not limited to the evaluation of planners.
%RP: I don't see why this needs to be restricted to "reasoning" tasks
Many reasoning tasks, including constraint solving and theorem
proving, are being evaluated by running solvers over problem instances
and reporting performance measures.  At the level of abstraction at
which our continuous evaluation system could be implemented, there is
no fundamental difference between the problem type ``deterministic
planning problem in PDDL 1.0'' and the problem type ``theorem of
first-order logic in TPTP format'' -- in both cases, the system can
collect problem classes and instances of this type and run them
through solvers that declare themselves to accept such inputs.  In
fact, other fields are already ahead of the planning community in
maintaining problem repositories as on Level 1 above
\cite{SS98,csplib,Asuncion+Newman:2007}. This means that there is a
potential for sharing development and maintenance costs for the
evaluation platform among different communities.

However, there are of course limitations to the type of problem for
which it makes sense to run a community-driven continuous evaluation.
For one thing, it must be acceptable in the community that every
system runs on the same hardware and software configuration, as
implemented in the virtual machine images.  On the other hand, our
system makes most sense where the ratio of problem classes to systems
is relatively high.  Neither of the two is true, for instance, for
most natural language processing competitions: different research
groups tend to use a variety of programming languages and development
environments to build their systems, and there are typically many more
systems in any competition than there are problem classes (text corpora).
However, our approach is completely consistent with the requirements
of a community where solving a single hard problem instance for the
first time counts as an achievement, such as in theorem proving.
